A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-11-19 01_Introduction.Rmd
some more text for the introduction

The spread of ideas in human populations over space and time is a major topic of Cultural Evolution research [@creanzaCulturalEvolutionaryTheory2017]. Archaeology has a special perspective to offer here: It's concerned with questions and data that can embrace continent size areas and millennia of cultural development and interaction [@garveyCurrentPotentialRoles2018].

>>>>

The spread of ideas in human populations over space and time is a major topic of *Cultural Evolution* research [@creanzaCulturalEvolutionaryTheory2017]. Archaeology has a special perspective to offer here: It's concerned with questions and data that can embrace continent size areas and millennia of cultural development and interaction [@garveyCurrentPotentialRoles2018]. Archaeological data now is mostly comprised of the material remains of human behaviour -- so the ruins of past architecture, individual lost or discarded artefacts and beyond that all kinds of waste and trash. Similarity between these artefacts within and beyond cultural-historical contexts are traditionally explained by *Cultural Transmission*: We rightfully expect humans to learn stories, traditions, ethical values and production techniques -- both functionally meaningful and seemingly pointless -- from others close to them. Material remains are a result of this long-term social exchange [@lymanChronometersUnitsEarly2000; @lymanCultureHistoricalBiological2001; @lymanRiseFallCulture1997; @obrienEpistemologicalNatureArchaeological2002].
